Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2014-08-27 gel_cond/trunk/generate.tex
fig:wholeprocess in column. A pannel with S(q) every 150s.

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}[
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]
	\begin{groupplot}[
	group style={
			group name=g, group size=1 by 2,
			vertical sep=3em,
			},
		width=0.4\textwidth,%
		height=0.2\textwidth+1em,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			xlabel={time (min)}, xmin=0,
			ymin=0, ymax=1, ylabel={aspect ratio},
			only marks,]
		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};

		\nextgroupplot[
			xmode=log, ymode=log,
			xlabel={$(t-t_0)/\tau_B$},
			ylabel=$\langle q\rangle\sigma$,
			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
			]
		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
		\addplot+[red, no marks, domain=50:300] {6*x^(-1/3)} node[midway, above]{$-1/3$};
	\end{groupplot}

	\matrix[
		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
		matrix anchor=north west,
		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
		] (m){
		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
		};
	\node[lab] at (m.north west) {a};
	\node[lab] at (g c1r1.outer north west) {b};
	\node[lab] at (g c1r2.outer north west) {c};
	\end{tikzpicture}
\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$). Origin of time is salt introduction. \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters. \textbf{b} Evolution of average aspect ratios of cluster containing more than 4 particles. \textbf{c} Growth of the characteristic wave number. Time origin is shifted to correspond to the melting of the Wigner crystal.}
\label{fig:wholeprocess}
\end{figure*}

>>>>

\begin{figure}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}[
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]
	\pgfplotscreateplotcyclelist{earthy}{%
	black,
	red!40!black,
	red!60!black,
	red!80!black,
	red,
	red!80!yellow,
	red!60!yellow,
	red!40!yellow,
	}
	\begin{groupplot}[
	group style={
			group name=g, group size=2 by 1,
			horizontal sep=4em,
			},
		width=0.5\columnwidth+1em,%
		height=10\baselineskip,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			xlabel={time (min)}, xmin=0,
			ymin=0, ymax=1, ylabel={aspect ratio},
			only marks,]
		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};

		\nextgroupplot[
			xmode=log, ymode=log,
			xlabel={$(t-t_0)/\tau_B$},
			ylabel=$\langle q\rangle\sigma$,
			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
			]
		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
		\addplot+[red, no marks, domain=20:200] {4*x^(-1/3)} node[midway, below left]{$-1/3$};
	\end{groupplot}

	\begin{axis}[name=Sq,
		anchor=below south west,
		at={(g c1r1.above north west)},
		xmin=0, xmax=13, ymin=0,
		xlabel=$q\sigma$, ylabel=$S(q)$,
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em},
		scale only axis,
		width=\columnwidth-3.5em,
		height=6\baselineskip,
		no marks, cycle list name=earthy]
		\foreach \ii in {1,2,...,7}
			\addplot table[y index=\ii] {155C_every150s.Sqs};
		\draw[<-] (axis cs:3.1,3.3) -- +(45:1em) node[right]{Wigner};
		\draw[<-,red!80!black] (axis cs:6.5,1.9) -- +(45:1em) node[right]{Hard sphere};
		\draw[<-,red!60!yellow] (axis cs:0.8,7.5) -- +(0:1em) node[right]{Gelation};
	\end{axis}

	\matrix[
		matrix of nodes, inner sep=0, column sep=0.01\textwidth, row sep=0.5em,
		matrix anchor=south west,
		%at={($(g c1r1.outer north west)$)},
		at={($(Sq.outer north west)$)},
		] (m){
		\SI{5}{\minute} & \SI{10}{\minute} \\
		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t024s.png}&
		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t044s.png}\\
		\SI{20}{\minute} & \SI{30}{\minute}\\
		\includegraphics[width=0.48\columnwidth]{155C_percolation_1645_p2size_t084s.png} &
		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t00s.png}\\
		 \SI{40}{\minute} & \SI{50}{\minute}\\
		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t20s.png}&
		\includegraphics[width=0.48\columnwidth]{155C_1715_ageing_p2size_t40s.png}\\
		};
	\node[lab] at (m.north west) {a};
	%\node[lab] at (g c1r1.outer north west) {b};
	%\node[lab] at (g c1r2.outer north west) {c};
	\end{tikzpicture}
\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$). Origin of time is salt introduction. \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters. \textbf{b} Evolution of average aspect ratios of cluster containing more than 4 particles. \textbf{c} Growth of the characteristic wave number. Time origin is shifted to correspond to the melting of the Wigner crystal.}
\label{fig:wholeprocess}
\end{figure}
